Proofs for ``Geometry of Local Spectral Clustering''

### 2021-01-15 jmlr/revision/proofs.tex
Completed bounds on population functionals of density clusters.

\section{Population functionals for density clusters}
\label{sec:density_cluster_population_functionals}
In this section, we prove Lemma~\ref{lem:density_cluster_local_spread} (in Section~\ref{subsec:density_cluster_local_spread}), Proposition~\ref{prop:density_cluster_normalized_cut} (in Section~\ref{subsec:density_cluster_ncut}), and Proposition~\ref{prop:density_cluster_conductance} (in Section~\ref{subsec:density_cluster_conductance}), by establishing bounds on the population-level local spread, normalized cut, and conductance of a thickened density cluster $\mc{C}_{\lambda,\sigma}$. In these proofs, we make use of some estimates on the volume of spherical caps, and we detail these in Section~\ref{subsec:spherical caps}; we also use some isoperimetric inequalities, which we detail in Section~\ref{subsec:isoperimetric_inequalities}. Throughout, we write $\nu_d := \nu(B(0,1))$ for the Lebesgue measure of a $d$-dimensional unit ball.

\subsection{Balls, Spherical Caps, and Associated Estimates}
\label{subsec:spherical caps}
In this section, we derive lower bounds on the volume of the intersection between two balls in $\Rd$, and the volume of a spherical cap. Results of this type are well-known, but since we could not find exactly the statements we desire, for completeness we also supply proofs. We use the notation $B(x,r)$ for a ball of radius $r$ centered at $x \in \Rd$, and $\mathrm{cap}_{r}(h)$ for a spherical cap of height $r$ and radius $r$. Recall that the Lebesgue measure of a spherical cap is
\begin{equation*}
\nu\bigl(\mathrm{cap}_r(h)\bigr) = \frac{1}{2} \nu_d r^d I_{1 - a}\left(\frac{d + 1}{2}; \frac{1}{2}\right)
\end{equation*}
where $a = (r - h)^2/r^2$, and
\begin{equation*}
I_{1 - a}(z,w) = \frac{\Gamma(z + w)}{\Gamma(z) \Gamma(w)} \int_{0}^{1 - a} u^{z - 1} (1 - u)^{w - 1} du.
\end{equation*}
is the cumulative distribution function of a $\mathrm{Beta}(z,w)$ distribution, evaluated at $1 - a$. (Here $\Gamma(\cdot)$ is the gamma function).
\begin{lemma}
	\label{lem:overlap_balls}
	For any $x,y \in \Rd$ and $r > 0$, it holds that
	\begin{equation}
	\label{eqn:overlap_balls_1}
	\nu\bigl(B(x,r) \cap B(y,r)\bigr) \geq \nu_d r^d\biggl(1 - \frac{\|x - y\|}{r} \sqrt{\frac{d + 2}{2\pi}}\biggr).
	\end{equation}
	For any $x,y \in \Rd$ and $r,\sigma > 0$ such that $\|x - y\| \leq \sigma$, it holds that,
	\begin{equation}
	\label{eqn:overlap_balls_2}
	\nu\bigl(B(x,r) \cap B(y,\sigma)\bigr) \geq \frac{1}{2} \nu_d r^d\biggl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\biggr).
	\end{equation}
\end{lemma}
\begin{lemma}
	\label{lem:volume_of_spherical_cap}
	For any $0 < h \leq r$, and $a = 1 - (2 r h - h^2)/r^2$,
	\begin{equation*}
	\nu\bigl(\mathrm{cap}_r(h)\bigr) \geq \frac{1}{2}\nu_dr^d\bigl(1 - 2\sqrt{a} \cdot \sqrt{\frac{d + 2}{2\pi}}\bigr)
	\end{equation*}
\end{lemma}
An immediate implication of~\eqref{eqn:overlap_balls_2} is that for any $x \in \mc{C}_{\lambda,\sigma}$,
\begin{equation}
\label{eqn:uniform_local_conductance}
\nu\bigl(B(x,r) \cap \mc{C}_{\lambda,\sigma}\bigr) \geq \frac{1}{2} \nu_d r^d\biggl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\biggr).
\end{equation}  
\begin{proof}[Proof (of Lemma~\ref{lem:overlap_balls})]
	First, we prove~\eqref{eqn:overlap_balls_1}. The intersection $B(x,r) \cap B(y,r)$ consists of two symmetric spherical caps, each with height $h = r - \frac{\|x - y\|}{2}$. 
	As a result, by Lemma~\ref{lem:volume_of_spherical_cap} we have
	\begin{equation*}
	\nu\bigl(B(x,r) \cap B(y,r)\bigr) \geq \nu_d r^d \bigl(1 - 2\sqrt{a} \cdot \sqrt{\frac{d + 2}{2\pi}}\bigr)
	\end{equation*}
	where $a = \|x - y\|^2/(4r^2)$, and the claim follows.

@@

\subsection{\textcolor{red}{Isoperimetric inequalities}}
\label{subsec:isoperimetric_inequalities}

For any set $\mc{C} \subseteq \Rd$ and $\sigma > 0$, recall that $\mc{C}_{\sigma} := \{x: \mathrm{dist}(x,\mc{C}) \leq \sigma\}$. We begin with an upper bound on the volume of $\mc{C}_{\sigma + \delta}$ as compared to $\mc{C}_{\sigma}$. 
\begin{lemma}
	\label{lem:external_isoperimetric_inequality}
	For any bounded set $\mc{C} \subseteq \Rd$ and  $\sigma, \delta > 0$, it holds that
	\begin{equation}
	\label{eqn:external_isoperimetric_inequality}
	\nu(\mc{C}_{\sigma + \delta}) \leq \nu(\mc{C}_{\sigma}) \cdot \Bigl(1 + \frac{\delta}{\sigma}\Bigr)^d.
	\end{equation}
\end{lemma}
To prove Lemma~\ref{lem:external_isoperimetric_inequality} for a general bounded set $\mc{C}$, we first construct a particular covering of $\mc{C}_{\sigma + \delta}$, then apply~\eqref{eqn:external_isoperimetric_inequality_1} to each set in the covering.

For $\delta \leq \sigma/d$ we have that $\bigl(1 + \delta/\sigma\bigr)^d \leq 1 + d \cdot \delta/(\sigma - d\delta)$, and we deduce from~\eqref{eqn:external_isoperimetric_inequality} that
\begin{equation}
\label{eqn:external_isoperimetric_inequality_2}
\nu(\mc{C}_{\sigma + \delta} \setminus \mc{C}_{\sigma}) = \nu(\mc{C}_{\sigma + \delta}) - \nu(\mc{C}_{\sigma}) \leq d \cdot \frac{\delta}{\sigma - d\delta} \cdot \nu(\mc{C}_{\sigma}).
\end{equation}
We use~\eqref{eqn:external_isoperimetric_inequality_2} along with Assumption~\ref{asmp:low_noise_density} to derive a density-weighted isoperimetric inequality. 
\begin{lemma}
	\label{lem:external_isoperimetric_inequality_density_weighted}
	Let $\mc{C}_{\lambda,\sigma}$ satisfy Assumption~\ref{asmp:bounded_density} and~\ref{asmp:low_noise_density} for some $\theta, \gamma$ and $\lambda_{\sigma}$. Then for any $0 < r \leq \sigma/d$, it holds that
	\begin{equation}
	\label{eqn:external_isoperimetric_inequality_density_weighted}
	\Pbb\bigl(\mc{C}_{\lambda,\sigma + r} \setminus \mc{C}_{\lambda,\sigma}\bigr) \leq \Bigl(1 + \frac{dr}{\sigma - dr}\Bigr) \cdot \frac{dr}{\sigma} \cdot \left(\lambda_{\sigma} - \theta\frac{r^{\gamma}}{\gamma + 1}\right) \cdot \nu(\mc{C}_{\lambda,\sigma}).
	\end{equation}
\end{lemma}

Before we prove Lemma~\ref{lem:external_isoperimetric_inequality}, we observe that in the special case where $\mc{C}$ is a single point---say $\mc{C} = \{0\}$--- the inequality~\eqref{eqn:external_isoperimetric_inequality} holds with equality. In this case $\mc{C}_{\sigma + \delta} = B(0,\sigma + \delta)$ and $\mc{C}_{\sigma} = B(0,\sigma)$, and
\begin{equation}
\label{eqn:external_isoperimetric_inequality_1}
\nu(\mc{C}_{\sigma + \delta}) = \nu_d (\sigma + \delta)^d = \nu_d \sigma^d \Bigl(1 + \frac{\delta}{\sigma}\Bigr)^d = \nu(\mc{C}_{\sigma}) \cdot \Bigl(1 + \frac{\delta}{\sigma}\Bigr)^d.
\end{equation}
\begin{proof}[Proof (of Lemma~\ref{lem:external_isoperimetric_inequality})] 
	Fix $\delta' > 0$, and take $\epsilon = \delta + \delta'$. We will show that
	\begin{equation*}
	\label{pf:external_isoperimetric_inequality}
	\nu(\mc{C}_{\sigma + \epsilon}) \leq \nu(\mc{C}_{\sigma}) \cdot \Bigl(1 + \frac{\epsilon}{\sigma}\Bigr)^d,
	\end{equation*}
	whence taking a limit as $\delta' \to 0$ yields the claim.

	To show~\eqref{pf:external_isoperimetric_inequality} for general closed and bounded $\mc{C}$, we need to construct a particular disjoint covering $\mc{A}_1(\sigma + \epsilon), \ldots, \mc{A}_N(\sigma + \epsilon)$ of $\mc{C}_{\sigma + \delta}$. To do so, we first take a finite set of points $x_1,\ldots,x_N$ such that the net $B(x_1,\sigma + \epsilon),\ldots,B(x_N,\sigma + \epsilon)$ covers $\mc{C}_{\sigma + \delta}$.  Note that such a covering exists for some finite $N = N(\epsilon)$ because $\mc{C}_{\sigma + \delta}$ is bounded, and the closure of $\mc{C}_{\sigma + \delta}$ is thus a compact subset of $\cup_{x \in \mc{C}} B(x,\sigma + \epsilon)$. Defining $\mc{A}_1(s), \ldots, \mc{A}_N(s)$ for a given $s > 0$ to be
	\begin{equation*}
	\mc{A}_1(s) := B(x_1,s),~~\textrm{and}~~ \mc{A}_{j + 1}(s) := B(x_{j + 1},s) \setminus \bigcup_{i = 1}^{j} B(x_i,s) ~~\textrm{for $j = 1,\ldots,N - 1$},
	\end{equation*}
	we have that $\mc{A}_1(\sigma + \epsilon),\ldots,\mc{A}_N(\sigma + \epsilon)$ is a disjoint covering of $\mc{C}_{\sigma + \delta}$, and so $\nu(\mc{C}_{\sigma + \delta}) \leq \sum_{j = 1}^{N} \nu(\mc{A}_j(\sigma + \epsilon))$.

	We claim that for all $j = 1,\ldots,N$, the function $s \mapsto \nu\bigl(\mc{A}_j(s)\bigr)/\nu\bigl(B(x_j,s)\bigr)$ is monotonically non-increasing in $s$. Once this claim is verified, it follows that
	\begin{equation*}
	\nu(\mc{A}_j(\sigma + \epsilon)) = \nu\bigl(B(x_j,\sigma + \epsilon)\bigr) \cdot \frac{\nu\bigl(\mc{A}_j(\sigma + \epsilon)\bigr)}{\nu\bigl(B(x_j,\sigma + \epsilon)\bigr)} \leq \Bigl(1 + \frac{\epsilon}{\sigma}\Bigr)^d \cdot  \nu\bigl(B(x_j,\sigma)\bigr) \cdot \frac{\nu\bigl(\mc{A}_j(\sigma)\bigr)}{\nu\bigl(B(x_j,\sigma)\bigr)} = \Bigl(1 + \frac{\epsilon}{\sigma}\Bigr)^d \cdot \nu\bigl(\mc{A}_j(\sigma)
	\end{equation*}
	and summing over $j$, we see that
	\begin{equation*}
	\nu(\mc{C}_{\sigma + \delta}) \leq \sum_{j = 1}^{N} \nu(\mc{A}_j(\sigma + \epsilon)) \leq \Bigl(1 + \frac{\epsilon}{\sigma}\Bigr)^d \sum_{j = 1}^{N} \nu\bigl(\mc{A}_j(\sigma) \leq \Bigl(1 + \frac{\epsilon}{\sigma}\Bigr)^d \mc{C}_{\sigma}
	\end{equation*}
	with the last inequality following since $\mc{A}_1(\sigma),\ldots,\mc{A}_N(\sigma)$ are disjoint subsets of $\mc{C}_{\sigma}$.

@@

\begin{proof}[Proof (of Lemma~\ref{lem:external_isoperimetric_inequality_density_weighted})]
	Fix $k \in \mathbb{N}$. To establish~\eqref{eqn:external_isoperimetric_inequality_density_weighted}, we partition $\mc{C}_{\lambda,\sigma + r} \setminus \mc{C}_{\lambda,\sigma}$ into thin tubes $\mc{T}_{1},\ldots,\mc{T}_{k}$, with the $j$th tube $\mc{T}_j$ defined as $\mc{T}_j := \mc{C}_{\lambda,\sigma + jr/k} \setminus \mc{C}_{\lambda,\sigma + (j - 1)r/k}.$ We upper bound the Lebesgue measure of each tube $\mc{T}_j$ using~\eqref{eqn:external_isoperimetric_inequality_2}:\footnote{Note that $\mc{C}$ must be bounded, since the density $f(x) \geq \lambda_{\sigma}$ for all $x \in \mc{C}$.}
	\begin{equation*}
	\nu(\mc{T}_j) \leq \frac{dr/k}{\sigma - dr/k} \nu(\mc{C}_{\lambda,\sigma + (j - 1)r/k}) \leq \frac{dr/k}{\sigma - dr/k} \nu(\mc{C}_{\lambda,\sigma + r}) \leq \Bigl(1 + \frac{dr}{\sigma - dr}\Bigr) \cdot \frac{dr/k}{\sigma - dr/k}  \cdot \nu(\mc{C}_{\lambda,\sigma}),
	\end{equation*}
	and the maximum density within each tube using~\ref{asmp:low_noise_density}:
	\begin{equation*}
	\max_{x \in \mc{T}_j} f(x) \leq \lambda_{\sigma} - \theta \Bigl(\frac{j - 1}{k}r\Bigr)^{\gamma};
	\end{equation*}
	combining these upper bounds, we see that
	\begin{equation}
	\label{pf:external_isoperimetric_inequality_density_weighted_1}
	\Pbb\bigl(\mc{C}_{\lambda,\sigma + r} \setminus \mc{C}_{\lambda,\sigma}\bigr) = \sum_{j = 1}^{k} \Pbb(\mc{T}_j) \leq \Bigl(1 + \frac{dr}{\sigma - dr}\Bigr) \cdot  \frac{dr/k}{\sigma - dr/k} \cdot \nu(\mc{C}_{\lambda,\sigma}) \cdot \biggl(\sum_{j = 0}^{k - 1}\lambda_{\sigma} -  \theta r^{\gamma} \Bigl(\frac{j}{k}\Bigr)^{\gamma} \biggr).
	\end{equation}
	Treating the sum in the previous expression as a Riemann sum of a non-increasing function evaluated at $0,\ldots,k -1$ gives the upper bound
	\begin{equation*}
	\sum_{j = 0}^{k - 1}\lambda_{\sigma} -  \theta r^{\gamma} \Bigl(\frac{j}{k}\Bigr)^{\gamma } \leq \lambda_{\sigma} + \int_{0}^{k - 1} \Bigl(\lambda_{\sigma} -  \theta r^{\gamma} \Bigl(\frac{x}{k}\Bigr)^{\gamma}\Bigr) \,dx \leq k\lambda_{\sigma} + (k - 1)\frac{\theta r^{\gamma}}{\gamma + 1} \Bigl(\frac{k - 1}{k}\Bigr)^{\gamma},
	\end{equation*}
	and plugging back in to~\eqref{pf:external_isoperimetric_inequality_density_weighted_1}, we obtain
	\begin{equation*}
	\Pbb\bigl(\mc{C}_{\lambda,\sigma + r} \setminus \mc{C}_{\lambda,\sigma}\bigr) \leq  \Bigl(1 + \frac{dr}{\sigma - dr}\Bigr) \cdot \frac{dr}{\sigma - dr/k} \nu(\mc{C}_{\lambda,\sigma}) \cdot \biggl(\lambda - \frac{\theta r^{\gamma}}{\gamma + 1} \cdot \Bigl(\frac{k - 1}{k}\Bigr)^{\gamma + 1} \biggl).
	\end{equation*}
	The above inequality holds for any $k \in \mathbb{N}$, and taking the limit of the right hand side as $k \to \infty$ yields the claim.
\end{proof}

>>>>

\section{Population functionals for density clusters}
\label{sec:density_cluster_population_functionals}
In this section, we prove Lemma~\ref{lem:density_cluster_local_spread} (in Section~\ref{subsec:density_cluster_local_spread}), Proposition~\ref{prop:density_cluster_normalized_cut} (in Section~\ref{subsec:density_cluster_ncut}), and Proposition~\ref{prop:density_cluster_conductance} (in Section~\ref{subsec:density_cluster_conductance}), by establishing bounds on the population-level local spread, normalized cut, and conductance of a thickened density cluster $\mc{C}_{\lambda,\sigma}$. In these proofs, we make use of some estimates on the volume of spherical caps (given in Section~\ref{subsec:spherical_caps}); some isoperimetric inequalities (given in Section~\ref{subsec:isoperimetric_inequalities}), and some reverse isoperimetric inequalities (given in Section~\ref{subsec:reverse_isoperimetric_inequalities}). Throughout, we write $\nu_d := \nu(B(0,1))$ for the Lebesgue measure of a $d$-dimensional unit ball.

\subsection{Balls, Spherical Caps, and Associated Estimates}
\label{subsec:spherical_caps}
In this section, we derive lower bounds on the volume of the intersection between two balls in $\Rd$, and the volume of a spherical cap. Results of this type are well-known, but since we could not find exactly the statements we desire, for completeness we also supply proofs. We use the notation $B(x,r)$ for a ball of radius $r$ centered at $x \in \Rd$, and $\mathrm{cap}_{r}(h)$ for a spherical cap of height $r$ and radius $r$. Recall that the Lebesgue measure of a spherical cap is
\begin{equation*}
\nu\bigl(\mathrm{cap}_r(h)\bigr) = \frac{1}{2} \nu_d r^d I_{1 - a}\left(\frac{d + 1}{2}; \frac{1}{2}\right)
\end{equation*}
where $a = (r - h)^2/r^2$, and
\begin{equation*}
I_{1 - a}(z,w) = \frac{\Gamma(z + w)}{\Gamma(z) \Gamma(w)} \int_{0}^{1 - a} u^{z - 1} (1 - u)^{w - 1} du.
\end{equation*}
is the cumulative distribution function of a $\mathrm{Beta}(z,w)$ distribution, evaluated at $1 - a$. (Here $\Gamma(\cdot)$ is the gamma function).
\begin{lemma}
	\label{lem:overlap_balls}
	For any $x,y \in \Rd$ and $r > 0$, it holds that
	\begin{equation}
	\label{eqn:overlap_balls_1}
	\nu\bigl(B(x,r) \cap B(y,r)\bigr) \geq \nu_d r^d\biggl(1 - \frac{\|x - y\|}{r} \sqrt{\frac{d + 2}{2\pi}}\biggr).
	\end{equation}
	For any $x,y \in \Rd$ and $r,\sigma > 0$ such that $\|x - y\| \leq \sigma$, it holds that,
	\begin{equation}
	\label{eqn:overlap_balls_2}
	\nu\bigl(B(x,r) \cap B(y,\sigma)\bigr) \geq \frac{1}{2} \nu_d r^d\biggl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\biggr).
	\end{equation}
\end{lemma}
\begin{lemma}
	\label{lem:volume_of_spherical_cap}
	For any $0 < h \leq r$, and $a = 1 - (2 r h - h^2)/r^2$,
	\begin{equation*}
	\nu\bigl(\mathrm{cap}_r(h)\bigr) \geq \frac{1}{2}\nu_dr^d\bigl(1 - 2\sqrt{a} \cdot \sqrt{\frac{d + 2}{2\pi}}\bigr)
	\end{equation*}
\end{lemma}
An immediate implication of~\eqref{eqn:overlap_balls_2} is that for any $x \in \mc{C}_{\lambda,\sigma}$,
\begin{equation}
\label{eqn:uniform_local_conductance}
\nu\bigl(B(x,r) \cap \mc{C}_{\lambda,\sigma}\bigr) \geq \frac{1}{2} \nu_d r^d\biggl(1 - \frac{r}{\sigma}\sqrt{\frac{d + 2}{2\pi}}\biggr).
\end{equation}  
\begin{proof}[Proof (of Lemma~\ref{lem:overlap_balls})]
	First, we prove~\eqref{eqn:overlap_balls_1}. The intersection $B(x,r) \cap B(y,r)$ consists of two symmetric spherical caps, each with height $h = r - \frac{\|x - y\|}{2}$. 
	As a result, by Lemma~\ref{lem:volume_of_spherical_cap} we have
	\begin{equation*}
	\nu\bigl(B(x,r) \cap B(y,r)\bigr) \geq \nu_d r^d \bigl(1 - 2\sqrt{a} \cdot \sqrt{\frac{d + 2}{2\pi}}\bigr)
	\end{equation*}
	where $a = \|x - y\|^2/(4r^2)$, and the claim follows.

@@

\subsection{Isoperimetric inequalities}
\label{subsec:isoperimetric_inequalities}
\citet{dyer1991} establish the following isoperimetric inequality for convex sets.
\begin{lemma}[Isoperimetry of a convex set.]
	\label{lem:convex_isoperimetric_inequality}
	For any partition $(\mc{R}_1,\mc{R}_2,\mc{R}_3)$ of a convex set $\mc{K} \subseteq \Rd$, it holds that
	\begin{equation*}
	\nu(\Omega_3) \geq 2\frac{\mathrm{dist}(\mc{R}_1, \mc{R}_2)}{\mathrm{diam}(\mc{K})} \min(\nu(\mc{R}_1), \nu(\mc{R}_2)).
	\end{equation*}
\end{lemma}
\citet{abbasi-yadkori2016a} points out that if $\mc{S}$ is the image of a convex set under a Lipschitz measure-preserving mapping $g: \Rd \to \Rd$, a similar inequality can be obtained.
\begin{corollary}[Isoperimetry of Lipschitz embeddings of convex sets.]
	\label{cor:nonconvex_isoperimetric_inequality}
	Suppose $\mc{S}$ is the image of a convex set $\mathcal{K}$ under a mapping $g:\Rd \to \Rd$ such that
	\begin{equation*}
	\|g(x) - g(y)\| \leq L \cdot \|x - y\|,~~\textrm{for all $x,y \in \mc{K}$, and}~~\det(\nabla g(x)) = 1~~\textrm{for all $x \in \mc{K}$.}
	\end{equation*}
	Then for any partition $(\Omega_1,\Omega_2,\Omega_3)$ of $\mc{S}$, 
	\begin{equation*}
	\nu(\Omega_3) \geq 2\frac{\mathrm{dist}(\Omega_1, \Omega_2)}{\diam(\mc{K}) L} \min(\nu(\Omega_1), \nu(\Omega_2)).
	\end{equation*}
\end{corollary}

\subsection{Reverse isoperimetric inequalities}
\label{subsec:reverse_isoperimetric_inequalities}

For any set $\mc{C} \subseteq \Rd$ and $\sigma > 0$, recall that $\mc{C}_{\sigma} := \{x: \mathrm{dist}(x,\mc{C}) \leq \sigma\}$. We begin with an upper bound on the volume of $\mc{C}_{\sigma + \delta}$ as compared to $\mc{C}_{\sigma}$. 
\begin{lemma}
	\label{lem:reverse_isoperimetric_inequality}
	For any bounded set $\mc{C} \subseteq \Rd$ and  $\sigma, \delta > 0$, it holds that
	\begin{equation}
	\label{eqn:reverse_isoperimetric_inequality}
	\nu(\mc{C}_{\sigma + \delta}) \leq \nu(\mc{C}_{\sigma}) \cdot \Bigl(1 + \frac{\delta}{\sigma}\Bigr)^d.
	\end{equation}
\end{lemma}
Lemma~\ref{lem:reverse_isoperimetric_inequality} should be interpreted as a reverse isoperimetric inequality. To see this, note that if $\delta \leq \sigma/d$ then $\bigl(1 + \delta/\sigma\bigr)^d \leq 1 + d \cdot \delta/(\sigma - d\delta)$, and we deduce from~\eqref{eqn:reverse_isoperimetric_inequality} that
\begin{equation}
\label{eqn:reverse_isoperimetric_inequality_2}
\nu(\mc{C}_{\sigma + \delta} \setminus \mc{C}_{\sigma}) = \nu(\mc{C}_{\sigma + \delta}) - \nu(\mc{C}_{\delta}) \leq \frac{d\delta}{\sigma - d\delta} \cdot \nu(\mc{C}_{\sigma}).
\end{equation}
We use~\eqref{eqn:reverse_isoperimetric_inequality_2} along with Assumption~\ref{asmp:low_noise_density} to derive a density-weighted reverse isoperimetric inequality. 
\begin{lemma}
	\label{lem:reverse_isoperimetric_inequality_density_weighted}
	Let $\mc{C}_{\lambda,\sigma}$ satisfy Assumption~\ref{asmp:bounded_density} and~\ref{asmp:low_noise_density} for some $\theta, \gamma$ and $\lambda_{\sigma}$. Then for any $0 < r \leq \sigma/d$, it holds that
	\begin{equation}
	\label{eqn:reverse_isoperimetric_inequality_density_weighted}
	\Pbb\bigl(\mc{C}_{\lambda,\sigma + r} \setminus \mc{C}_{\lambda,\sigma}\bigr) \leq \Bigl(1 + \frac{dr}{\sigma - dr}\Bigr) \cdot \frac{dr}{\sigma} \cdot \left(\lambda_{\sigma} - \theta\frac{r^{\gamma}}{\gamma + 1}\right) \cdot \nu(\mc{C}_{\lambda,\sigma}).
	\end{equation}
\end{lemma}
\begin{proof}[Proof (of Lemma~\ref{lem:reverse_isoperimetric_inequality})] 
	Fix $\delta' > 0$, and take $\epsilon = \delta + \delta'$. We will show that
	\begin{equation*}
	\label{pf:reverse_isoperimetric_inequality}
	\nu(\mc{C}_{\sigma + \epsilon}) \leq \nu(\mc{C}_{\sigma}) \cdot \Bigl(1 + \frac{\epsilon}{\sigma}\Bigr)^d,
	\end{equation*}
	whence taking a limit as $\delta' \to 0$ yields the claim.

	To show~\eqref{pf:reverse_isoperimetric_inequality} for general closed and bounded $\mc{C}$, we need to construct a particular disjoint covering $\mc{A}_1(\sigma + \epsilon), \ldots, \mc{A}_N(\sigma + \epsilon)$ of $\mc{C}_{\sigma + \delta}$. To do so, we first take a finite set of points $x_1,\ldots,x_N$ such that the net $B(x_1,\sigma + \epsilon),\ldots,B(x_N,\sigma + \epsilon)$ covers $\mc{C}_{\sigma + \delta}$.  Note that such a covering exists for some finite $N = N(\epsilon)$ because $\mc{C}_{\sigma + \delta}$ is bounded, and the closure of $\mc{C}_{\sigma + \delta}$ is thus a compact subset of $\cup_{x \in \mc{C}} B(x,\sigma + \epsilon)$. Defining $\mc{A}_1(s), \ldots, \mc{A}_N(s)$ for a given $s > 0$ to be
	\begin{equation*}
	\mc{A}_1(s) := B(x_1,s),~~\textrm{and}~~ \mc{A}_{j + 1}(s) := B(x_{j + 1},s) \setminus \bigcup_{i = 1}^{j} B(x_i,s) ~~\textrm{for $j = 1,\ldots,N - 1$},
	\end{equation*}
	we have that $\mc{A}_1(\sigma + \epsilon),\ldots,\mc{A}_N(\sigma + \epsilon)$ is a disjoint covering of $\mc{C}_{\sigma + \delta}$, and so $\nu(\mc{C}_{\sigma + \delta}) \leq \sum_{j = 1}^{N} \nu(\mc{A}_j(\sigma + \epsilon))$.

	We claim that for all $j = 1,\ldots,N$, the function $s \mapsto \nu\bigl(\mc{A}_j(s)\bigr)/\nu\bigl(B(x_j,s)\bigr)$ is monotonically non-increasing in $s$. Once this claim is verified, it follows that
	\begin{equation*}
	\nu(\mc{A}_j(\sigma + \epsilon)) = \nu\bigl(B(x_j,\sigma + \epsilon)\bigr) \cdot \frac{\nu\bigl(\mc{A}_j(\sigma + \epsilon)\bigr)}{\nu\bigl(B(x_j,\sigma + \epsilon)\bigr)} \leq \Bigl(1 + \frac{\epsilon}{\sigma}\Bigr)^d \cdot  \nu\bigl(B(x_j,\sigma)\bigr) \cdot \frac{\nu\bigl(\mc{A}_j(\sigma)\bigr)}{\nu\bigl(B(x_j,\sigma)\bigr)} = \Bigl(1 + \frac{\epsilon}{\sigma}\Bigr)^d \cdot \nu\bigl(\mc{A}_j(\sigma)
	\end{equation*}
	and summing over $j$, we see that
	\begin{equation*}
	\nu(\mc{C}_{\sigma + \delta}) \leq \sum_{j = 1}^{N} \nu\bigl(\mc{A}_j(\sigma + \epsilon)\bigr) \leq \Bigl(1 + \frac{\epsilon}{\sigma}\Bigr)^d \cdot \sum_{j = 1}^{N} \nu\bigl(\mc{A}_j(\sigma)\bigr) \leq \Bigl(1 + \frac{\epsilon}{\sigma}\Bigr)^d \mc{C}_{\sigma},
	\end{equation*}
	with the last inequality following since $\mc{A}_1(\sigma),\ldots,\mc{A}_N(\sigma)$ are disjoint subsets of $\mc{C}_{\sigma}$.

@@

\begin{proof}[Proof (of Lemma~\ref{lem:reverse_isoperimetric_inequality_density_weighted})]
	Fix $k \in \mathbb{N}$. To establish~\eqref{eqn:reverse_isoperimetric_inequality_density_weighted}, we partition $\mc{C}_{\lambda,\sigma + r} \setminus \mc{C}_{\lambda,\sigma}$ into thin tubes $\mc{T}_{1},\ldots,\mc{T}_{k}$, with the $j$th tube $\mc{T}_j$ defined as $\mc{T}_j := \mc{C}_{\lambda,\sigma + jr/k} \setminus \mc{C}_{\lambda,\sigma + (j - 1)r/k}.$ We upper bound the Lebesgue measure of each tube $\mc{T}_j$ using~\eqref{eqn:reverse_isoperimetric_inequality_2}:\footnote{Note that $\mc{C}$ must be bounded, since the density $f(x) \geq \lambda_{\sigma}$ for all $x \in \mc{C}$.}
	\begin{equation*}
	\nu(\mc{T}_j) \leq \frac{dr/k}{\sigma - dr/k} \nu(\mc{C}_{\lambda,\sigma + (j - 1)r/k}) \leq \frac{dr/k}{\sigma - dr/k} \nu(\mc{C}_{\lambda,\sigma + r}) \leq \Bigl(1 + \frac{dr}{\sigma - dr}\Bigr) \cdot \frac{dr/k}{\sigma - dr/k}  \cdot \nu(\mc{C}_{\lambda,\sigma}),
	\end{equation*}
	and the maximum density within each tube using~\ref{asmp:low_noise_density}:
	\begin{equation*}
	\max_{x \in \mc{T}_j} f(x) \leq \lambda_{\sigma} - \theta \Bigl(\frac{j - 1}{k}r\Bigr)^{\gamma};
	\end{equation*}
	combining these upper bounds, we see that
	\begin{equation}
	\label{pf:reverse_isoperimetric_inequality_density_weighted_1}
	\Pbb\bigl(\mc{C}_{\lambda,\sigma + r} \setminus \mc{C}_{\lambda,\sigma}\bigr) = \sum_{j = 1}^{k} \Pbb(\mc{T}_j) \leq \Bigl(1 + \frac{dr}{\sigma - dr}\Bigr) \cdot  \frac{dr/k}{\sigma - dr/k} \cdot \nu(\mc{C}_{\lambda,\sigma}) \cdot \biggl(\sum_{j = 0}^{k - 1}\lambda_{\sigma} -  \theta r^{\gamma} \Bigl(\frac{j}{k}\Bigr)^{\gamma} \biggr).
	\end{equation}
	Treating the sum in the previous expression as a Riemann sum of a non-increasing function evaluated at $0,\ldots,k -1$ gives the upper bound
	\begin{equation*}
	\sum_{j = 0}^{k - 1}\lambda_{\sigma} -  \theta r^{\gamma} \Bigl(\frac{j}{k}\Bigr)^{\gamma } \leq \lambda_{\sigma} + \int_{0}^{k - 1} \Bigl(\lambda_{\sigma} -  \theta r^{\gamma} \Bigl(\frac{x}{k}\Bigr)^{\gamma}\Bigr) \,dx \leq k\lambda_{\sigma} + (k - 1)\frac{\theta r^{\gamma}}{\gamma + 1} \Bigl(\frac{k - 1}{k}\Bigr)^{\gamma},
	\end{equation*}
	and plugging back in to~\eqref{pf:reverse_isoperimetric_inequality_density_weighted_1}, we obtain
	\begin{equation*}
	\Pbb\bigl(\mc{C}_{\lambda,\sigma + r} \setminus \mc{C}_{\lambda,\sigma}\bigr) \leq  \Bigl(1 + \frac{dr}{\sigma - dr}\Bigr) \cdot \frac{dr}{\sigma - dr/k} \nu(\mc{C}_{\lambda,\sigma}) \cdot \biggl(\lambda - \frac{\theta r^{\gamma}}{\gamma + 1} \cdot \Bigl(\frac{k - 1}{k}\Bigr)^{\gamma + 1} \biggl).
	\end{equation*}
	The above inequality holds for any $k \in \mathbb{N}$, and taking the limit of the right hand side as $k \to \infty$ yields the claim.
\end{proof}
